A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Add operation mix table

\begin{table}[ht]\resizebox{\columnwidth}{!}{%
\begin{tabular}{lll}\hline
Events & Core Eval Call \% & Package Eval Call \% \\ \hline
\EventsMinRangeA--\EventsMaxRangeA & \EventsCoreEvalPercA & \EventsPackageEvalPercA \\
\EventsMinRangeB--\EventsMaxRangeB & \EventsCoreEvalPercB & \EventsPackageEvalPercB \\
\EventsMinRangeC--\EventsMaxRangeC & \EventsCoreEvalPercC & \EventsPackageEvalPercC \\
\end{tabular}} \label{table:event-distribution}
\caption{Distribution of events in \eval calls across Core and Package}
\end{table}

@@

Unlike Javascript, R packages also call native code for access to efficient
numerical and statistical routines. We intercept all calls to R functions and
native functions from the programs and \eval calls. In the whole corpus there
are \AllClosureCallCount calls to R functions and \AllNativeCallCount to native
code. Of those, \eval contribute to only \EvalClosureCallCount calls to R
functions and \EvalNativeCallCount to native code.

>>>>

\begin{table}[ht]\resizebox{\columnwidth}{!}{%
\begin{tabular}{lll}\hline
Events & Core Eval Call \% & Package Eval Call \% \\ \hline
\EventsMinRangeA--\EventsMaxRangeA & \EventsCoreEvalPercA & \EventsPackageEvalPercA \\
\EventsMinRangeB--\EventsMaxRangeB & \EventsCoreEvalPercB & \EventsPackageEvalPercB \\
\EventsMinRangeC--\EventsMaxRangeC & \EventsCoreEvalPercC & \EventsPackageEvalPercC \\ \hline
\end{tabular}} \label{table:event-distribution}
\caption{Distribution of events in \eval calls across Core and Package}
\end{table}

@@

%%Unlike Javascript, R packages also call native code for access to efficient
%%numerical and statistical routines. We intercept all calls to R functions and
%%native functions from the programs and \eval calls. In the whole corpus there
%%are \AllClosureCallCount calls to R functions and \AllNativeCallCount to native
%%code. Of those, \eval contribute to only \EvalClosureCallCount calls to R
%%functions and \EvalNativeCallCount to native code.
%%
%%\begin{table}[ht]\resizebox{\columnwidth}{!}{%
%%    \begin{tabular}{lll}\hline
%%      Source & Primitive Functions & R Functions & Native Functions \\ \hline
%%      Core & \CorePrimitiveFunctionCount & \CoreRFunctionCount & \CoreNativeFunctionCount \\
%%      CRAN & \PackagePrimitiveFunctionCount & \PackageRFunctionCount & \PackageNativeFunctionCount \\
%%      All  & \AllPrimitiveFunctionCount & \AllRFunctionCount & \AllNativeFunctionCount \\
%%    \end{tabular}} \label{table:operation-distribution}
%%  \caption{Distribution of operation calls to \eval calls across Core and Package}
%%\end{table}
